Project Membach

### 2020-05-26 project.Rmd
correctly use train set

setwd("/media/data/Documents/Uni/spatiotemp/villalobos/project/")
if (!exists("domain")) {
  # UCCS
  domain <- c(-350000,350000); pattern <- "UCCS.*\\.csv"; name <- "UCCS"; description <- "Uccle, Bruxelles"; proj_file <- 'proj.uccs.RData'
  # MEMS
  domain <- c(-7200,7200); pattern <- "MEM.*\\.csv"; name <- "MEM"; description <- "Membach"; proj_file <- 'proj.mems.RData'
}
if (exists("proj_file")) {
  #load(paste0("/media/data/Documents/Uni/spatiotemp/villalobos/project/", proj_file))
  # save.image(paste0("/media/data/Documents/Uni/spatiotemp/villalobos/project/", proj_file))
}

@@

seis.h <- merge(seis.h, seis.dst.fix, all=T)
remove(seis.after, seis.before, seis.dst.fix)
gc()
```

@@

```{r test_train split ts, include=FALSE}
seis.h.start <- as_datetime('2018-10-29T00:00:00')
seis.h.end <- as_datetime('2020-03-02T00:00:00') - seconds(1)
seasonality.period <- 24
seasonality.xlab <- "Days"
seasonality.aggregate <- function(ds) na.aggregate(seis.h.ts, function(x) floor(x/14))
seasonality.period <- 168
seasonality.xlab <- "Weeks"
seasonality.aggregate <- function(ds) na.aggregate(ds, floor)
seis.h.ts <- build_ts(seis.h, periods = c(seasonality.period), start = seis.h.start, end = seis.h.end, force_ms = T)

@@

seis.test.start <- seis.test.split
seis.test.end <- as_datetime('2020-05-04T00:00:00') - seconds(1)
seis.h.test <- build_ts(seis.h, periods = c(seasonality.period), start = seis.h.start, end = seis.test.end, force_ms = T)
seis.h.test <- window(seis.h.test, start = c(end(seis.h.train)[1] + 1, 1))
seis.test.length <- length(seis.h.test)
```

```{r periodgram}
library(spec)
pgram <- spec.pgram(seis.h.train, main="periodgram", detrend=F, demean=T, na.action=na.aggregate)
topfreq <- pgram$freq[order(pgram$spec, decreasing = T)][1:100]
topseas <- 1/topfreq
topseas.h <- topseas/1

filter_freq <- (pgram$spec > (mean(pgram$spec) + sd(pgram$spec)*2)) 
top95pc <- pgram$spec[filter_freq]
top95freq <- pgram$freq[filter_freq][order(top95pc, decreasing = T)]
top95pc <- pgram$spec[filter_freq][order(top95pc, decreasing = T)]
top95seas.s <- 1/top95freq
top95seas.s
top95seas.h <- top95seas.s/1
top95pc/sd(pgram$spec)
top95seas.h

@@

```{r plot data with (p)acf}
seis.h.24 <- build_ts(seis.h, periods = c(24), start = seis.h.start, end = seis.h.end)
seasonplot(seis.h.24, type="l", col=rainbow(7))
legend("topleft", legend=weekdays(seis.h.start + (as.difftime(c(0:6), units="days"))), col=rainbow(7), lty=1, cex=0.8)

plot_grid(
  autoplot(seis.h.ts, main = "Hourly seismic movement", xlab = seasonality.xlab, ylab = "mean movement (nm)"),
  gghistogram(seis.h.ts, add.normal = T) + xlab("mean movement (nm)"),
  nrow = 2)
plot_grid(
  autoplot(acf(seis.h.ts, na.action=na.pass, plot=F, lag.max=seasonality.period)) + scale_x_continuous(),
  autoplot(pacf(seis.h.ts, na.action=na.pass, plot=F, lag.max=seasonality.period)) + scale_x_continuous(),
  nrow = 2)

```
Once notice the composition is additive (the fluctuations does not seem to grow with the trend)
```{r decompose}
dec.addi <- decompose(seasonality.aggregate(seis.h.ts))
autoplot(dec.addi) + labs(title="Decomposition of additive time series", subtitle = paste0("Seasonality ", seasonality.period))
dec.multi <- decompose(log(seasonality.aggregate(seis.h.ts)))
autoplot(dec.multi) + labs(title="Decomposition of multiplicative time series (log-scale additive)", subtitle = paste0("Seasonality ", seasonality.period))
plot_grid(
  autoplot(acf(dec.addi$random, na.action=na.omit, plot=F)) + scale_x_continuous(),
  autoplot(acf(dec.multi$random, na.action=na.omit, plot=F)) + scale_x_continuous(),
  nrow = 2)
plot_grid(
  autoplot(pacf(dec.addi$random, na.action=na.omit, plot=F)) + scale_x_continuous(),
  autoplot(pacf(dec.multi$random, na.action=na.omit, plot=F)) + scale_x_continuous(),
  nrow = 2)
```

@@

```{r linear trend}
p <- floor(seasonality.period/2)
weights <- rep(1/(2*p+1), times=2*p+1)
trend <- stats::filter(seasonality.aggregate(seis.h.ts), sides=2, filter = weights)
```

@@

  mse <- mean(diff^2, na.rm = T)
  mae <- mean(abs(diff), na.rm = T)
  rmse <- sqrt(mse)
  R2 <- 1-(sum((diff)^2, na.rm = T)/sum((base-mean(base))^2, na.rm = T))
  errorstring <- paste0("MSE=", mse, "    MAE=", mae, "    RMSE=", rmse, "    R2=", R2)
  print(errorstring)

@@

```{r trend MA}
f <- seasonality.period
weights.s <- c(0.5, rep(1,f-1), 0.5)/f
trend.s <- stats::filter(seasonality.aggregate(seis.h.ts), side=2, filter=weights.s)

@@

```{r trend figure}
detrended <- seasonality.aggregate(seis.h.ts)-trend.s
detrended <- window(detrended, end = c(end(detrended)[1], seasonality.period), extend=T)
matrix <- t(matrix(data = detrended, nrow = seasonality.period))
seasonality.figure <- as.ts(colMeans(matrix, na.rm = T))
seasonality <- rep(seasonality.figure, length(detrended)/length(seasonality.figure))[1:length(trend.s)]
```

@@

```{r residuals}
residuals <- seasonality.aggregate(seis.h.ts) - trend.s - seasonality

@@

plots <- show_overlap_and_diff(
  seis.h.ts, ts, xlab=seasonality.xlab,
  base.desc = "original series",
  compare.desc = "reconstructed series",
  overlap.ylab = "Mean hourly movement (nm)",
  diff.title = "Difference between ts",
  diff.ylab = "nm", diff.ylab.sec="% over ts span",
  diff.ylab.sec.accuracy = .01
)
plot_grid(plots[[1]], plots[[2]], nrow = 2)

plots <- show_overlap_and_diff(
  seis.h.ts, dec.addi$trend+dec.addi$seasonal+dec.addi$random, xlab=seasonality.xlab,
  base.desc = "original series",
  compare.desc = "reconstructed series",
  overlap.ylab = "Mean hourly movement (nm)",
  diff.title = "Difference between ts",
  diff.ylab = "nm", diff.ylab.sec="% over ts span",
  diff.ylab.sec.accuracy = .01
)
plot_grid(plots[[1]], plots[[2]], nrow = 2)

@@

aggregated <- seasonality.aggregate(seis.h.ts)
season.24 <- trend_season(aggregated, 24)
season.168 <- trend_season(aggregated-season.24$seasonal, 168)

>>>>

setwd("/media/data/Documents/Uni/spatiotemp/villalobos/project/")
if (!exists("domain")) {
  # UCCS
  domain <- c(-350000,350000); pattern <- "UCCS.*\\.csv"; name <- "UCCS"; description <- "Uccle, Bruxelles"; proj_file <- 'proj.uccs.RData'
  # MEMS
  domain <- c(-7200,7200); pattern <- "MEM.*\\.csv"; name <- "MEM"; description <- "Membach"; proj_file <- 'proj.mems.RData'
}
if (exists("proj_file")) {
  load(paste0("/media/data/Documents/Uni/spatiotemp/villalobos/project/", proj_file))
  # save.image(paste0("/media/data/Documents/Uni/spatiotemp/villalobos/project/", proj_file))
}

@@

seis.h <- merge(seis.h, seis.dst.fix, all=T)
remove(seis.after, seis.before, seis.dst.fix)

# invalid_values <- seis.h$mean_movement_s > 200
# seis.h <-
#   seis.h %>%
#   mutate(mean_movement_s=replace(mean_movement_s, invalid_values, NA)) %>%
#   drop_na()
# remove(invalid_values)

gc()
```

@@

```{r test_train split ts, include=FALSE}
seis.h.start <- as_datetime('2018-10-29T00:00:00')
seis.h.end <- as_datetime('2020-03-02T00:00:00') - seconds(1)
seasonality.period <- 24
seasonality.xlab <- "Days"
seasonality.aggregate <- function(ds) na.aggregate(ds, function(x) floor(x/14))
seasonality.period <- 168
seasonality.xlab <- "Weeks"
seasonality.aggregate <- function(ds) na.aggregate(ds, floor)
seis.h.ts <- build_ts(seis.h, periods = c(seasonality.period), start = seis.h.start, end = seis.h.end, force_ms = T)

@@

seis.test.start <- seis.test.split
seis.test.end <- seis.test.start + days(7*18) - seconds(1)
seis.h.test <- build_ts(seis.h, periods = c(seasonality.period), start = seis.train.start, end = seis.test.end, force_ms = T)
seis.h.test <- window(seis.h.test, start = c(end(seis.h.train)[1] + 1, 1))
seis.test.length <- length(seis.h.test)
```

```{r periodgram}
library(spec)
pgram <- spec.pgram(build_ts(seis.h, start = seis.train.start, end = seis.train.end), main="periodgram", detrend=F, demean=T, na.action=na.aggregate)
topfreq <- pgram$freq[order(pgram$spec, decreasing = T)][1:100]
topseas <- 1/topfreq
topseas.h <- topseas/3600

filter_freq <- (pgram$spec > (mean(pgram$spec) + sd(pgram$spec)*2)) 
top95pc <- pgram$spec[filter_freq]
top95freq <- pgram$freq[filter_freq][order(top95pc, decreasing = T)]
top95pc <- pgram$spec[filter_freq][order(top95pc, decreasing = T)]
cat("SD ratio\n")
(top95pc - mean(pgram$spec))/sd(pgram$spec)
top95seas.s <- 1/top95freq
cat("Raw frequency by unit\n")
top95seas.s
top95seas.h <- top95seas.s/3600
cat("Frequency by unit\n")
top95seas.h

@@

```{r plot data with (p)acf}
seis.h.24 <- build_ts(seis.h.train, periods = c(24))
seasonplot(seis.h.24, type="l", col=rainbow(7))
legend("topleft", legend=weekdays(seis.train.start + (as.difftime(c(0:6), units="days"))), col=rainbow(7), lty=1, cex=0.8)

plot_grid(
  autoplot(seis.h.train, main = "Hourly seismic movement", xlab = seasonality.xlab, ylab = "mean movement (nm)"),
  gghistogram(seis.h.train, add.normal = T) + xlab("mean movement (nm)"),
  nrow = 2)
plot_grid(
  autoplot(acf(seis.h.train, na.action=na.pass, plot=F, lag.max=seasonality.period)) + scale_x_continuous(),
  autoplot(pacf(seis.h.train, na.action=na.pass, plot=F, lag.max=seasonality.period)) + scale_x_continuous(),
  nrow = 2)

```
Once notice the composition is additive (the fluctuations does not seem to grow with the trend)
```{r decompose}
dec.addi <- decompose(seasonality.aggregate(seis.h.train))
autoplot(dec.addi) + labs(title="Decomposition of additive time series", subtitle = paste0("Seasonality ", seasonality.period))
dec.multi <- decompose(log(seasonality.aggregate(seis.h.train)))
autoplot(dec.multi) + labs(title="Decomposition of multiplicative time series (log-scale additive)", subtitle = paste0("Seasonality ", seasonality.period))
plot_grid(
  autoplot(acf(dec.addi$random, na.action=na.omit, plot=F)) + scale_x_continuous(),
  autoplot(acf(dec.multi$random, na.action=na.omit, plot=F)) + scale_x_continuous(),
  nrow = 2)
plot_grid(
  autoplot(pacf(dec.addi$random, na.action=na.omit, plot=F)) + scale_x_continuous(),
  autoplot(pacf(dec.multi$random, na.action=na.omit, plot=F)) + scale_x_continuous(),
  nrow = 2)
```

@@

```{r linear trend}
p <- floor(seasonality.period/2)
weights <- rep(1/(2*p+1), times=2*p+1)
trend <- stats::filter(seasonality.aggregate(seis.h.train), sides=2, filter = weights)
```

@@

  mse <- mean(diff^2, na.rm = T)
  mae <- mean(abs(diff), na.rm = T)
  rmse <- sqrt(mse)
  R2 <- 1-(sum((diff)^2, na.rm = T)/sum((base-mean(base))^2, na.rm = T))
  errorstring <- paste0("MSE=", mse, "    MAE=", mae, "    RMSE=", rmse, "    R2=", R2)
  cat("Errors: ", compare.desc, "\n")
  cat("\t","MSE=", mse, "    MAE=", mae, "    RMSE=", rmse, "    R2=", R2, "\n")

@@

```{r trend MA}
f <- seasonality.period
weights.s <- c(0.5, rep(1,f-1), 0.5)/f
trend.s <- stats::filter(seasonality.aggregate(seis.h.train), side=2, filter=weights.s)

@@

```{r trend figure}
detrended <- seasonality.aggregate(seis.h.train)-trend.s
detrended <- window(detrended, end = c(end(detrended)[1], seasonality.period), extend=T)
matrix <- t(matrix(data = detrended, nrow = seasonality.period))
seasonality.figure <- as.ts(colMeans(matrix, na.rm = T))
seasonality <- rep(seasonality.figure, length(detrended)/length(seasonality.figure))[1:length(trend.s)]
```

@@

```{r residuals}
residuals <- seasonality.aggregate(seis.h.train) - trend.s - seasonality

@@

plots <- show_overlap_and_diff(
  seis.h.train, ts, xlab=seasonality.xlab,
  base.desc = "original series",
  compare.desc = "reconstructed serie (manual)",
  overlap.ylab = "Mean hourly movement (nm)",
  diff.title = "Difference between ts",
  diff.ylab = "nm", diff.ylab.sec="% over ts span",
  diff.ylab.sec.accuracy = .01
)
plot_grid(plots[[1]], plots[[2]], nrow = 2)

plots <- show_overlap_and_diff(
  seis.h.train, dec.addi$trend+dec.addi$seasonal+dec.addi$random, xlab=seasonality.xlab,
  base.desc = "original series",
  compare.desc = "reconstructed serie (decompose additive)",
  overlap.ylab = "Mean hourly movement (nm)",
  diff.title = "Difference between ts",
  diff.ylab = "nm", diff.ylab.sec="% over ts span",
  diff.ylab.sec.accuracy = .01
)
plot_grid(plots[[1]], plots[[2]], nrow = 2)

@@

aggregated <- seasonality.aggregate(seis.h.train)
season.24 <- trend_season(aggregated, 24)
season.168 <- trend_season(aggregated-season.24$seasonal, 168)

### 2020-05-26 project.mems.Rmd
correctly use train set

>>>>

```{r transformation}
plot(seis.h, xaxt="n", type="l")
axis.POSIXct(1, at=seq.POSIXt(from=seis.h.start, to=seis.h.end, by = "1 month"), format="%m-%y", cex=0.8)

hist(seis.h.train)
plot(log(seis.h.train))
hist(log(seis.h.train))
train.bc.lambda <- BoxCox.lambda(seis.h.train)
train.bc <- BoxCox(seis.h.train, train.bc.lambda)
plot(train.bc)
gghistogram(train.bc, add.normal = T)
gg_qqplot(seis.h.train) + 
        labs(title="Q-Q plot for training dataset") + ylab("Sample quantiles")
gg_qqplot(log(seis.h.train)) + 
        labs(title="Q-Q plot for log(training) dataset") + ylab("Sample quantiles")
gg_qqplot(train.bc) + 
        labs(title="Q-Q plot for BoxCox(training) dataset") + ylab("Sample quantiles")
```

```{r acf-pacf}
train.bc %>% ggtsdisplay(lag.max = 168*5)
train.bc %>% diff() %>% ggtsdisplay(lag.max = 168*5)
train.bc %>% diff(lag=24) %>% ggtsdisplay(lag.max = 168)
train.bc %>% diff() %>% diff(lag=24) %>% ggtsdisplay(lag.max = 168)
train.bc %>% diff(lag=168) %>% ggtsdisplay(lag.max = 168*5)
train.bc %>% diff() %>% diff(lag=168) %>% ggtsdisplay(lag.max = 168*5) # arima (0,1,0)(0,1,1)[168]
train.bc %>% diff() %>% diff(lag=168) %>% ggtsdisplay(lag.max = 168) # arima (0,1,0)(0,1,1)[168]
# acf cuts off after p=168, pacf shows peaks each 168
train.bc %>% diff() %>% diff(lag=24) %>% diff(lag=168) %>% ggtsdisplay(lag.max = 168*5)
```

```{r arima}
to_test <- list(
  c(0,1,0,0,1,1)
)

if (!exists("models")){
  models <- list()
}
for (model in to_test) {
  # model <- c(4,1,2,0,1,0)
  fit.name <- paste0("fit", paste0(model, collapse = ""))
  forecast.name <- paste0("forecast", paste0(model, collapse = ""))
  print("SARIMA(" %s+% paste0(model[1:3], collapse = ",") %s+% ")(" %s+% paste0(model[4:6], collapse = ",") %s+% ")[" %s+% frequency(seis.h.train) %s+% "]")
  if (!(fit.name %in% names(models))) {
    models[[fit.name]] <- Arima(seis.h.train, model[1:3], model[4:6], lambda=train.bc.lambda)
  }
  if (!(forecast.name %in% names(models))) {
    models[[forecast.name]] <- forecast(models[[fit.name]], h=168*18, lambda=train.bc.lambda)
  }
}
#models[["fitauto"]] <- auto.arima(train.bc, D=1, approx=F, trace = T)
#models[["forecastauto"]] <- forecast(models[["fitauto"]], h=168*18)  
#models[["fit311010"]] <- models[["fitauto"]]
#models[["fit412010"]] <- fit
#models[["forecast412010"]] <- forecast(models[["fit412010"]], h=168*18)

for (model in to_test) {
  # model <- c(4,1,2,0,1,0)
  fit.name <- paste0("fit", paste0(model, collapse = ""))
  forecast.name <- paste0("forecast", paste0(model, collapse = ""))
  print("SARIMA(" %s+% paste0(model[1:3], collapse = ",") %s+% ")(" %s+% paste0(model[4:6], collapse = ",") %s+% ")[" %s+% frequency(seis.h.train) %s+% "]")
  if ((fit.name %in% names(models))) {  if ((forecast.name %in% names(models))) {
    plotting.model <- models[[fit.name]]
    plotting.forecast <- models[[forecast.name]]
    checkresiduals(plotting.model)
    residuals.acf <- autoplot(acf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=168*5)) + scale_x_continuous() + labs(title = paste0("Series: residuals of ", plotting.forecast$method))
    residuals.pacf <- autoplot(pacf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=168*5)) + scale_x_continuous() + labs(title = paste0("Series: residuals of ", plotting.forecast$method))
    print(plot_grid(residuals.acf, residuals.pacf, nrow=2))
    print(plot_forecast(plotting.forecast) + 
      autolayer(seis.h.test, series="Original"))
    plots <- show_overlap_and_diff(
      seis.h.train, plotting.forecast$fitted, xlab=seasonality.xlab,
      base.desc = "original series",
      compare.desc = paste0("refit with ", plotting.forecast$method),
      overlap.ylab = "Mean hourly movement (nm)",
      diff.title = "Difference between ts",
      diff.ylab = "nm", diff.ylab.sec="% over ts span",
      diff.ylab.sec.accuracy = .01
    )

    print(plot_grid(plots[[1]], plots[[2]], nrow = 2))
    accuracy(plotting.forecast, seis.h.test)
    # qqPlot(plotting.model$residuals, main = paste0("Q-Q plot for ", plotting.forecast$method), xlab = "residuals")
    print(gg_qqplot(plotting.model$residuals) + 
        labs(title=paste0("Q-Q plot for ", plotting.forecast$method, " residuals")) + ylab("Residuals quantiles")
    )
  }}
}

```

```{r arima on seasonality}
autoplot(residuals+trend.s)
residuals.bc.lambda <- BoxCox.lambda(residuals+trend.s)
residuals.bc <- BoxCox(residuals+trend.s, residuals.bc.lambda)
residuals.bc %>% ggtsdisplay(lag.max = 168*5)
residuals.bc %>% diff() %>% ggtsdisplay(lag.max = 168*5)
residuals.bc %>% diff(lag=24) %>% ggtsdisplay(lag.max = 168)
residuals.bc %>% diff() %>% diff(lag=24) %>% ggtsdisplay(lag.max = 168)
residuals.bc %>% diff(lag=168) %>% ggtsdisplay(lag.max = 168*5)
residuals.bc %>% diff() %>% diff(lag=168) %>% ggtsdisplay(lag.max = 168*5) # arima (0,1,0)(0,1,1)[168]
residuals.bc %>% diff() %>% diff(lag=168) %>% ggtsdisplay(lag.max = 168) # arima (0,1,0)(0,1,1)[168]
# acf cuts off after p=168, pacf shows peaks each 168
residuals.bc %>% diff() %>% diff(lag=24) %>% diff(lag=168) %>% ggtsdisplay(lag.max = 168*5)

gg_qqplot(residuals) + 
  labs(title=paste0("Q-Q plot for ", plotting.forecast$method, " residuals")) + ylab("Residuals quantiles")

a <- Arima(residuals, order = c(1,0,0), seasonal = c(0,0,0), lambda=residuals.bc.lambda)
afor <- forecast(a, h=168*18, lambda=residuals.bc.lambda)

plotting.model <- a
plotting.forecast <- afor

autoplot(plotting.model) + xlab("Week")

gg_qqplot(plotting.model$residuals) + 
  labs(title=paste0("Q-Q plot for ", plotting.forecast$method, " residuals")) + ylab("Residuals quantiles")
checkresiduals(plotting.model$residuals)
Box.test(plotting.forecast$model$residuals, type="L")
residuals.acf <- autoplot(acf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=168*5)) + scale_x_continuous() + labs(title = paste0("Series: residuals of ", plotting.forecast$method))
residuals.pacf <- autoplot(pacf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=168*5)) + scale_x_continuous() + labs(title = paste0("Series: residuals of ", plotting.forecast$method))
plot_grid(residuals.acf, residuals.pacf, nrow=2)

plot_forecast(plotting.forecast) + 
  autolayer(seis.h.test, series="Test") + 
  autolayer(seis.h.train, series="Train")
plots <- show_overlap_and_diff(
  seis.h.train, plotting.forecast$fitted, xlab=seasonality.xlab,
  base.desc = "train series",
  compare.desc = paste0("refit with ", plotting.forecast$method),
  overlap.ylab = "Mean hourly movement (nm)",
  diff.title = "Difference between ts",
  diff.ylab = "nm", diff.ylab.sec="% over ts span",
  diff.ylab.sec.accuracy = .01
)
plot_grid(plots[[1]], plots[[2]], nrow = 2)
plots <- show_overlap_and_diff(
  seis.h.test[1:length(plotting.forecast$mean)], plotting.forecast$mean, xlab=seasonality.xlab,
  base.desc = "test series",
  compare.desc = paste0("refit with ", plotting.forecast$method),
  overlap.ylab = "Mean hourly movement (nm)",
  diff.title = "Difference between ts",
  diff.ylab = "nm", diff.ylab.sec="% over ts span",
  diff.ylab.sec.accuracy = .01
)
plot_grid(plots[[1]], plots[[2]], nrow = 2)
accuracy(plotting.forecast, seis.h.test)

```

```{r auto arima}
#fit <- auto.arima(seis.h.train, d=1, D=1, max.p=5, max.q=2, max.P=5, max.Q=2, max.order=10, trace = T, parallel = T)
```

```{r mstl on msts}
seis.h.train.m <- msts(seis.h.train, c(24, 168))
seis.mstl <- seis.h.train.m %>% mstl(s.window="periodic", lambda=train.bc.lambda) #c(15, 7))
seis.mstl.fc <- forecast(seis.mstl, h=168*18, lambda=train.bc.lambda)

plot(InvBoxCox(seis.mstl[,2], lambda=train.bc.lambda), main="trend")
lines(trend.s, col="red")
plot(InvBoxCox(rowSums(seis.mstl[,3:4]), lambda=train.bc.lambda), main="seasonality",type="l")
lines(seasonality, col="red")
plot(InvBoxCox(seis.mstl[,5], lambda=train.bc.lambda),  main="residuals")
lines(residuals, col="red")

plotting.model <- seis.mstl
plotting.forecast <- seis.mstl.fc

autoplot(plotting.model) + xlab("Week")

gg_qqplot(plotting.model[,5]) + 
  labs(title=paste0("Q-Q plot for ", seis.mstl.fc$method, " residuals")) + ylab("Residuals quantiles")
checkresiduals(plotting.model[,5])
Box.test(plotting.forecast$model$residuals, type="L")
residuals.acf <- autoplot(acf(plotting.model[,5], na.action = na.pass, plot=F, lag.max=168*5)) + scale_x_continuous() + labs(title = paste0("Series: residuals of ", plotting.forecast$method))
residuals.pacf <- autoplot(pacf(plotting.model[,5], na.action = na.pass, plot=F, lag.max=168*5)) + scale_x_continuous() + labs(title = paste0("Series: residuals of ", plotting.forecast$method))
plot_grid(residuals.acf, residuals.pacf, nrow=2)

plot_forecast(plotting.forecast) + 
  autolayer(seis.h.test, series="Test") + 
  autolayer(seis.h.train, series="Train")
plots <- show_overlap_and_diff(
  seis.h.train, plotting.forecast$fitted, xlab=seasonality.xlab,
  base.desc = "train series",
  compare.desc = paste0("refit with ", plotting.forecast$method),
  overlap.ylab = "Mean hourly movement (nm)",
  diff.title = "Difference between ts",
  diff.ylab = "nm", diff.ylab.sec="% over ts span",
  diff.ylab.sec.accuracy = .01
)
plot_grid(plots[[1]], plots[[2]], nrow = 2)
plots <- show_overlap_and_diff(
  seis.h.test[1:length(plotting.forecast$mean)], plotting.forecast$mean, xlab=seasonality.xlab,
  base.desc = "test series",
  compare.desc = paste0("refit with ", plotting.forecast$method),
  overlap.ylab = "Mean hourly movement (nm)",
  diff.title = "Difference between ts",
  diff.ylab = "nm", diff.ylab.sec="% over ts span",
  diff.ylab.sec.accuracy = .01
)
plot_grid(plots[[1]], plots[[2]], nrow = 2)
accuracy(plotting.forecast, seis.h.test)

bptests <- data.frame(lag=integer(), `p-value`=numeric())
for (i in 1:10){
  bptests[nrow(bptests) + 1, ] <- c(i, Box.test(plotting.model[,5], lag = i, fitdf = 0, type = "Box-Pierce")$p.value)
}
bptests.plot <- 
  ggplot(bptests, aes(lag, `p.value`), pch="o") + 
    geom_point() + ylim(0,1) +
    labs(title="Box-Pierce tests for lags 1 to 10") +
    geom_hline(yintercept=0.05, linetype="dotted", color = "blue") +
    scale_x_continuous(breaks=1:10)
bptests.plot

```

```{r save RData, include=FALSE}
gc()
proj_file <- 'proj.mems.RData'
save.image(proj_file)
```
